The Effect of Elections and Changed Governments on Discussion in the Australian Federal Parliament (1901--2017)

### 2018-11-13 outputs/docs/events/paper.Rmd
Update Appendix B

The Parliament website is missing the Hansard PDFs for the following dates in the Senate: 
1988-12-21, 1988-12-20, 1988-12-19, 1988-12-16, 1988-12-15, 1988-12-14, 1988-12-13, 1988-12-12, 2000-10-12, 2000-06-19, 2004-08-09, .

@@

There is one unaccounted for differences in 1920, 1921, 1935, 1942, 1948, 1951, 1991, 2003, 2004, and there are two unaccounted for in 1985 and four unaccounted for in 2012

In the Senate, the PDF for 10 August 1917 may be the wrong one? It says it is for 10 Jan 1918 on the cover sheet, but there's not even an entry for 10 Jan 1918...??? Very odd....

@@

```{r scrapingexample, echo=TRUE, eval = FALSE}
library(purrr)
library(tidyverse)

# Create lists of URLs to scrape and file names to save the PDF as
data_to_scrape <- read_csv("csv_of_address_to_visit_and_save_names.csv")
# Pull out the two pieces
address_to_visit <- data_to_scrape$URL
save_name <- data_to_scrape$file_name
# Add a containing folder to the save_names
save_name <- paste0("pdfs/", save_name)
# Create that containing folder if necessary
dir.create("pdfs")

# The function that will visit address_to_visit and save to save_name file
visit_address_and_save_PDF <-
  function(name_of_address_to_visit,
           name_of_where_to_save) {
    # Do the actual downloading of the PDF
    download.file(name_of_address_to_visit, name_of_where_to_save)
    # Helpful so that you know progress when running it on all the records
    print(paste("Done with", name_of_where_to_save, "at", Sys.time()))  
    # Space out your requests so you don't overwhelm the website
    Sys.sleep(sample(15:30, 1)) 
  }

# Make the function more resistent to issues
safe_visit_address_and_save_PDF <- safely(visit_address_and_save_PDF)

# Walk through the lists and get the PDFs
walk2(address_to_visit, save_name, ~ safe_visit_address_and_save_PDF(.x, .y))
```

@@

```{r frontmatterexample, echo=TRUE, eval = FALSE}
library(furrr) # May need the devtools version devtools::install_github("DavisVaughan/furrr")
library(lubridate)
library(pdftools)
library(stringi)
library(tidyverse)
library(tictoc)
library(tm)
# Set up furrr to use multiple processors
plan(multiprocess)

# Create the lists of PDFs to read and file names to save text as
use_this_path_to_get_pdfs  <- "/Volumes/Hansard/pdfs/federal/hor"
use_this_path_to_save_csv_files  <- "/Volumes/Hansard/parsed/federal/hor"

# Get list of Hansard PDF filenames
file_names <-
  list.files(
    path = use_this_path_to_get_pdfs,
    pattern = "*.pdf",
    recursive = TRUE,
    full.names = TRUE
  )
file_names <- file_names %>% sample() # Randomise the order
# Modify the savenames
save_names <- file_names %>%
  str_replace(use_this_path_to_get_pdfs, "") %>%
  str_replace(".pdf", ".csv")
save_names <- paste0(use_this_path_to_save_csv_files, save_names)

#### Create the function that will be applied to the files ####
get_text_from_PDFs <-
  function(name_of_input_PDF_file,
           name_of_output_csv_file) {
    pdf_document <- pdf_text(name_of_input_PDF_file)
    # Convert to tibble so that tidyverse can be used
    pdf_document_tibble <- tibble(text = pdf_document)
    rm(pdf_document)
    # Each row is now a page of the PDF
    # Adding a column of the row numbers allows you to keep track of the page numbers
    pdf_document_tibble$pageNumbers <- 1:nrow(pdf_document_tibble)
    # Separate each line (of each page) into own row
    pdf_document_tibble <-
      separate_rows(pdf_document_tibble, text, sep = "\\n")

    # Identify page headers and footers and remove them
    pdf_document_tibble <- pdf_document_tibble %>%
      group_by(pageNumbers) %>%
      mutate(lineNumber = 1:n()) %>% # This gives you a line numbering for each page
      mutate(lastLine = n()) %>% # This tells you the number of the last line in each page
      ungroup()

    ## Identify front matter and remove it
    # Primarily identify the start of talking based on the first occurence of 'Mr SPEAKER'. 
    # It seems pretty common, but there are some misses (e.g. 1991-01-22). 
    # Use various backups
    pdf_document_tibble <- pdf_document_tibble %>%
      mutate(
        firstSpeakerRow = str_detect(text, "SPEAKER"),
        firstPresidentRow = str_detect(text, "PRESIDENT"),
        firstJointHouseRow = str_detect(text, "JOINT HOUSE"),
        firstTookTheChairRow = str_detect(text, "took the chair"),
        firstTheChairAtRow = str_detect(text, "the chair at")
      )
    pdf_document_tibble$firstSpeakerRow[pdf_document_tibble$firstSpeakerRow == FALSE] <- NA
    pdf_document_tibble$firstPresidentRow[pdf_document_tibble$firstPresidentRow == FALSE] <- NA
    pdf_document_tibble$firstJointHouseRow[pdf_document_tibble$firstJointHouseRow == FALSE] <- NA
    pdf_document_tibble$firstTookTheChairRow[pdf_document_tibble$firstTookTheChairRow == FALSE] <- NA
    pdf_document_tibble$firstTheChairAtRow[pdf_document_tibble$firstTheChairAtRow == FALSE] <- NA

    # Get the row and corresponding page and then filter to only pages from that page
    row_of_first_SPEAKER <-
      pdf_document_tibble$firstSpeakerRow[pdf_document_tibble$firstSpeakerRow == TRUE] %>% which() %>% first()
    row_of_first_PRESIDENT <-
      pdf_document_tibble$firstPresidentRow[pdf_document_tibble$firstPresidentRow == TRUE] %>% which() %>% first()
    row_of_first_JOINTHOUSE <-
      pdf_document_tibble$firstJointHouseRow[pdf_document_tibble$firstJointHouseRow == TRUE] %>% which() %>% first()
    row_of_first_TookTheChair <-
      pdf_document_tibble$firstTookTheChairRow[pdf_document_tibble$firstTookTheChairRow == TRUE] %>% which() %>% first()
    row_of_first_TheChairAt <-
      pdf_document_tibble$firstTheChairAtRow[pdf_document_tibble$firstTheChairAtRow == TRUE] %>% which() %>% first()

    first_page_of_interest_SPEAKER <-
      pdf_document_tibble[row_of_first_SPEAKER, "pageNumbers"] %>% as.integer()
    first_page_of_interest_PRESIDENT <-
      pdf_document_tibble[row_of_first_PRESIDENT, "pageNumbers"] %>% as.integer()
    first_page_of_interest_JOINTHOUSE <-
      pdf_document_tibble[row_of_first_JOINTHOUSE, "pageNumbers"] %>% as.integer()
    first_page_of_interest_TookTheChair <-
      pdf_document_tibble[row_of_first_TookTheChair, "pageNumbers"] %>% as.integer()
    first_page_of_interest_TheChairAt <-
      pdf_document_tibble[row_of_first_TheChairAt, "pageNumbers"] %>% as.integer()

    first_page_of_interest_JOINTHOUSE <-
      (first_page_of_interest_JOINTHOUSE + 1)  %>% as.integer()

    filter_from_here <-
      case_when(
        !is.na(first_page_of_interest_TookTheChair) ~ first_page_of_interest_TookTheChair,
        !is.na(first_page_of_interest_TheChairAt) ~ first_page_of_interest_TheChairAt,
        !is.na(first_page_of_interest_SPEAKER) ~ first_page_of_interest_SPEAKER,
        !is.na(first_page_of_interest_PRESIDENT) ~ first_page_of_interest_PRESIDENT,
        TRUE ~ first_page_of_interest_JOINTHOUSE
      )

    pdf_document_tibble <- pdf_document_tibble %>%
      filter(pageNumbers >= filter_from_here) %>%
      select(-firstSpeakerRow,
             -firstPresidentRow,
             -firstJointHouseRow,
             -firstTookTheChairRow,
             -firstTheChairAtRow)

    # Save file
    write_csv(pdf_document_tibble, name_of_output_csv_file)
    # Helpful to know where you're up to
    print(paste0("Done with ", name_of_output_csv_file, " at ", Sys.time()))
  }

#### Walk through the lists and parse the PDFs ####
# Avoid errors
safely_get_text_from_PDFs <- safely(get_text_from_PDFs)

tic("Furrr walk2 stringr")
future_walk2(file_names,
             save_names,
             ~ safely_get_text_from_PDFs(.x, .y),
             .progress = TRUE)
toc()

@@

UP TO HERE

**[TBD].**

>>>>

The Parliament website is missing the Hansard PDFs for the following dates in the Senate: 
1988-12-21, 1988-12-20, 1988-12-19, 1988-12-16, 1988-12-15, 1988-12-14, 1988-12-13, 1988-12-12, 2000-10-12, 2000-06-19, 2004-08-09.

@@

There is one unaccounted for difference in 1920, 1921, 1935, 1942, 1948, 1951, 1991, 2003, 2004, and there are two unaccounted for in 1985 and four unaccounted for in 2012.

In the Senate, the PDF for 10 August 1917 may be the wrong one. It says it is for 10 January 1918 on the cover sheet, but there's not an entry for 10 January 1918.

@@

```{r scrapingexample, echo=TRUE, eval = FALSE}
visit_address_and_save_PDF <-
  function(name_of_address_to_visit,
           name_of_where_to_save) {
    # Do the actual downloading of the PDF
    download.file(name_of_address_to_visit, name_of_where_to_save)
    # Helpful so that you know progress when running it on all the records
    print(paste("Done with", name_of_where_to_save, "at", Sys.time()))  
    # Space out your requests so you don't overwhelm the website
    Sys.sleep(sample(15:30, 1)) 
  }
```

@@

```{r frontmatterexample, echo=TRUE, eval = FALSE}

get_text_from_PDFs <-
  function(name_of_input_PDF_file,
           name_of_output_csv_file) {
    pdf_document <- pdf_text(name_of_input_PDF_file)
    # Convert to tibble so that tidyverse can be used
    pdf_document_tibble <- tibble(text = pdf_document)
    rm(pdf_document)
    # Each row is now a page of the PDF
    # Adding a column of the row numbers allows you to keep track of the page numbers
    pdf_document_tibble$pageNumbers <- 1:nrow(pdf_document_tibble)
    # Separate each line (of each page) into own row
    pdf_document_tibble <-
      separate_rows(pdf_document_tibble, text, sep = "\\n")
    # Identify page headers and footers and remove them
    pdf_document_tibble <- pdf_document_tibble %>%
      group_by(pageNumbers) %>%
      mutate(lineNumber = 1:n()) %>% # This gives you a line numbering for each page
      mutate(lastLine = n()) %>% # This tells you the number of the last line in each page
      ungroup()
    ## Identify front matter and remove it
    pdf_document_tibble <- pdf_document_tibble %>%
      mutate(
        firstSpeakerRow = str_detect(text, "SPEAKER")
      )
    pdf_document_tibble$firstSpeakerRow[pdf_document_tibble$firstSpeakerRow == FALSE] <- NA
    # Get the row and corresponding page and then filter to only pages from that page
    row_of_first_SPEAKER <-
      pdf_document_tibble$firstSpeakerRow[pdf_document_tibble$firstSpeakerRow == TRUE] %>% which() %>% first()
    first_page_of_interest_SPEAKER <-
      pdf_document_tibble[row_of_first_SPEAKER, "pageNumbers"] %>% as.integer()
    filter_from_here <-
      case_when(
        !is.na(first_page_of_interest_SPEAKER) ~ first_page_of_interest_SPEAKER
      )
    pdf_document_tibble <- pdf_document_tibble %>%
      filter(pageNumbers >= filter_from_here) %>%
      select(-firstSpeakerRow)
    # Save file
    write_csv(pdf_document_tibble, name_of_output_csv_file)
    # Helpful to know where you're up to
    print(paste0("Done with ", name_of_output_csv_file, " at ", Sys.time()))
  }

@@

Then the rows need to be combined:
```{r combinerows, echo=TRUE, eval = FALSE}
split_columns <-
  function(name_of_input_csv_file,
           name_of_output_csv_file) {
    # Read in the csv, based on the filename list
    csv_with_rows_to_combine <-
      read_csv(name_of_input_csv_file,
               trim_ws = FALSE,
               col_types = cols())
    # Remove any extra whitespace i.e. two or more spaces and spaces at either end. 
    # Yes, I know that I turned this off in the read_csv, but it's better to be 
    #explicit because the whitespace is useful sometimes.
    csv_with_rows_to_combine$text <-
      str_squish(csv_with_rows_to_combine$text)
    # Put everything onto one line, which allows us to rejoin words that have been 
    #split across two lines e.g. Mon- ica
    csv_with_rows_to_combine <- csv_with_rows_to_combine %>%
      mutate(text = str_replace_all(text, "-$", "MONICA"))
    full_days_hansard <- csv_with_rows_to_combine %>%
      select(-pageNumbers) %>%
      summarise(text = paste(text, collapse = " ")) %>%
      mutate(text = str_replace_all(text, "MONICA ", "")) %>%
      mutate(text = str_replace_all(text, "[:space:]-(?=[:alpha:])", " - "))
    rm(csv_with_rows_to_combine)
    write_csv(full_days_hansard, name_of_output_csv_file)
    print(paste0("Done with ", name_of_output_csv_file, " at ", Sys.time()))
  }
```

Finally, we can fix the spelling:
```{r fixspelling, echo=TRUE, eval = FALSE}
fix_spelling <-
  function(name_of_input_csv_file,
           name_of_output_csv_file) {
    csv_to_clean <-
      read_csv(name_of_input_csv_file,
               trim_ws = FALSE,
               col_types = cols())
    #Fix the spelling
    csv_to_clean$text <-
      stri_replace_all_regex(
        csv_to_clean$text,
        "\\b" %s+% fix_wrong_spellings$original %s+% "\\b",
        fix_wrong_spellings$corrected,
        vectorize_all = FALSE
      )
    # Save file
    write_csv(csv_to_clean, name_of_output_csv_file)
    print(paste0("Done with ", name_of_output_csv_file, " at ", Sys.time()))
  }
```
